Supplemental Information

### 2021-07-26 supplement/supplement-main.Rmd
minor text edits

---
title: "Supplemental Materials"
subtitle: "Untitled vaccination intuitive theory paper"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
date: "Jul 21, 2021 (DRAFT)"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
bibliography: references.bib
csl: pnas.csl
figsintext : yes
always_allow_html: true
header-includes:
 \usepackage{float}
---

@@

>>>>

---
title: "Supplemental Information"
subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
bibliography: references.bib
csl: pnas.csl
figsintext : yes
always_allow_html: true
header-includes:
 \usepackage{float}
---

@@

# Data Availability

Data and code for this project are available at: https://github.com/derekpowell/int-theory-vacc

Preregistrations information is available at: https://osf.io/uemq4
